---
site: blogdown:::blogdown_site
---

### Recruitment {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/recruitment.Rmd', eval = TRUE}
```

### CONSORT {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/consort.Rmd', eval = TRUE}
```

### EQ5D {.tabset .tabset-fade .tabset-pills}

```{r child='results_cohort/eq5d.Rmd', eval = TRUE}
```

### EORTC QLC C30 {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/eortc_qlq_c30.Rmd', eval = FALSE}
```

### EORTC QLC BR23 {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/eortc_qlq_br23.Rmd', eval = FALSE}
```

### EORTC QLC ELD15 {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/eortc_qlq_eld15.Rmd', eval = FALSE}
```

### Therapy Assessment {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/therapy_assessment.Rmd', eval = FALSE}
```

### Encdocrine Therapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/endocrine_therapy.Rmd', eval = FALSE}
```

### Radiotherapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/radiotherapy.Rmd', eval = FALSE}
```

### Chemotherapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/chemotherapy.Rmd', eval = FALSE}
```

### Trastuzumab {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/trastuzumab.Rmd', eval = FALSE}
```

### Surgery {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/surgery.Rmd', eval = FALSE}
```

### Clinical Assessment - PET {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/clinical_assessment_pet.Rmd', eval = FALSE}
```

### Clinical Assessment - Non-PET {.tabset .tabset-fade .tabset-pills}
```{r child='results_cohort/clinical_assessment_pet.Rmd', eval = FALSE}
```
