---
site: blogdown:::blogdown_site
---

```{r echo = FALSE, eval = TRUE}
## Generate files
cmd <- c('cd results_missing && ./populate.sh && cd ..')
system(cmd)

```

The patterns of missing data are summarised for each set of questionnaires and details of the multiple imputation methods are then provided.


### EQ5D {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_eq5d.Rmd', eval = TRUE}
```

### EORTC QLC C30 {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_eortc_qlq_c30.Rmd', eval = TRUE}
```

### EORTC QLC BR23 {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_eortc_qlq_br23.Rmd', eval = TRUE}
```

### EORTC QLC ELD15 {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_eortc_qlq_eld15.Rmd', eval = TRUE}
```

### Therapy Assessment {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_therapy_assessment.Rmd', eval = FALSE}
```

### Encdocrine Therapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_endocrine_therapy.Rmd', eval = FALSE}
```

### Radiotherapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_radiotherapy.Rmd', eval = FALSE}
```

### Chemotherapy {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_chemotherapy.Rmd', eval = FALSE}
```

### Trastuzumab {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_trastuzumab.Rmd', eval = FALSE}
```

### Surgery {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_surgery.Rmd', eval = FALSE}
```

### Clinical Assessment - PET {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_clinical_assessment_pet.Rmd', eval = FALSE}
```

### Clinical Assessment - Non-PET {.tabset .tabset-fade .tabset-pills}
```{r child='results_missing/patterns_clinical_assessment_pet.Rmd', eval = FALSE}
```
