Adverse events are summarised below.

```{r results_adverse_events, echo = FALSE, warning = FALSE, message = FALSE, results = 'show', cache = FALSE, fig_width = 10, fig_height = 20, eval = TRUE}
master$adverse_events_ae %>%
    mutate(ae_event = tolower(ae_event)) %$%
    table(ae_event) %>%
    as.data.frame() %>%
    kable(colnames = c('Adverse Event (as recorded)', 'Frequency'),
          caption = 'Adverse Events as recorded with their frequency.')

```

When Adverse Events are recorded a `start_dt` and `end_dt` are recorded along with an `ongoing` field (binary ticked or not), thus it is possible to determine how many events are still considered to be being experienced by study participants by looking at whether `ongoing` has been ticked and/or whether an `end_dt` (end date) has been recorded.


```{r results_adverse_events_ongoing, echo = FALSE, warning = FALSE, message = FALSE, results = 'show', cache = FALSE, fig_width = 10, fig_height = 20, eval = TRUE}
master$adverse_events_ae %>%
    mutate(has_end_dt = ifelse(!is.na(end_dt),
                               yes = TRUE,
                               no  = FALSE)) %$%
    table(ongoing, has_end_dt) %>%
    kable(colnames = c('Ongoing', 'No End Date', 'End Date'),
          caption = 'Reconciling end dates with on-going status')

n_not_ongoing_missing_end_date <- master$adverse_events_ae %>%
                                  mutate(has_end_dt = ifelse(!is.na(end_dt),
                                                             yes = TRUE,
                                                             no  = FALSE)) %>%
                                  dplyr::filter(ongoing == 'Not Ticked' & has_end_dt == TRUE) %>%
                                  nrow()

```

As can be seen there are no instances where adverse events have been recorded as `ongoing` (i.e. `Ticked`) that have had an end date recorded against them, however there are `r n_not_ongoing_missing_end_date` instances where the `ongoing`field has *not*  been ticked (i.e. `Not Ticked`) suggesting that the Adverse Event is not ongoing when it was recorded, but no end date has been recorded.


It may be of interest to look at Adverse Events by one or more grouping factor.  The Statistical Analysis Plan
