Recruitment is plotted and tabulated across all sites below (which is interactive/dynamic and can be zoomed and information provided when you move the mouse over it), followed by summaries by site.  Note that the facetted plot showing screening and recruitment by site has a 'free' y-axis so that the plots are ledgible (if they were forced to all be the same sites that recruited very few participants would not be easy to read).



```{r results_cohort_recruitment, echo = FALSE, warning = FALSE, message = FALSE, results = 'show', cache = FALSE, fig_height = 20, fig_width = 10, eval = TRUE}
screening_recruitment$plotly_screened_recruited_all
screening_recruitment$table_screened_recruited_month %>%
    dplyr::filter(Site == 'All') %>%
    kable(caption = 'Screening and Recruitment across all sites by m1onth')
## ToDo - Leave this in for now, ultimately it will be replaced by htmlwidget that allows selection
##        of site as per below.
screening_recruitment$plot_screened_recruited_site
screening_recruitment$table_screened_recruited_month %>%
    dplyr::filter(Site != 'All') %>%
    kable(caption = 'Screening and Recruitment by site and month')

```

```{r results_cohort_recruitment_each_site, echo = FALSE, warning = FALSE, message = FALSE, results = 'show', cache = FALSE, fig_height = 20, fig_width = 10, eval = FALSE}
## See https://shiny.rstudio.com/articles/interactive-docs.html
##
## Currently fails with...
##
## > rmarkdown::run('age-gap.Rmd')
## Listening on http://127.0.0.1:6275
## 
## Warning in readLines(if (is.character(input2)) { :
##   cannot open file '/tmp/Rtmpd5mHQF/sections/analysis/recruitment.Rmd': No such file or directory
##
## Quitting from lines 2-2 (/tmp/Rtmpd5mHQF/sections/analysis/recruitment.Rmd)
## Quitting from lines NA-8 (/tmp/Rtmpd5mHQF/sections/analysis/recruitment.Rmd)
## Warning: Error in readLines: cannot open the connection
sites <- names(screening_recruitment$plot_screened_recruited_each_site)
selectInput('site', label = 'Site',
            choices = sites, selected = 'sheffield')
renderText(site)
renderPlot(screening_recruitment$plot_screened_recruited_each_site[[site]])

```
