### More Tables

For convenience a large number of tables are also generated for editing and usage elsewhere.

#### Baseline Characteristics

##### Continuous Variables

Combined table for continuous baseline characteristics.


```{r table_baseline_continuous, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
```

##### Factor Variables

Combined table for factor baseline characteristics.

```{r table_baseline_factor, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
```

#### EQ5D

Table of EQ5D responses for all time points.

```{r table_eq5d, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
test <- age_gap %>%
        dplyr::filter(!is.na(primary_treatment)) %>%
        ungroup() %>%
        ctru::table_summary(df        = .,
                            lookup    = master$lookups_fields,
                            id        = individual_id,
                            select    = c(## eq5d_number,
                                          eq5d_score,
                                          mobility,
                                          self_care,
                                          usual_activity,
                                          pain_discomfort,
                                          anxiety_depression),
                            time      = event_name,
                            group     = primary_treatment,
                            nomissing = FALSE,
                            digits    = 2,
                            reshape   = NULL)
## Reshape the factor table and print
spread(test$factor,
       value,
       n_prop,
       fill = "0 (0.00)") %>%
    mutate(Dimension = label,
           Event     = event_name) %>%
    ## You can reorder this table by choosing which of the two lines below you wish to order by
    arrange(Dimension, primary_treatment, event_name) %>%
    ## arrange(Dimension, event_name, primary_treatment) %>%
    dplyr::select(Dimension, primary_treatment, Event,
                  None, Slight, Moderate, Severe, Extreme, `<NA>`, -label) %>%
    kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
          caption = "EQ5D responses by Time-Point and Primary Treatment Group.")
## Tabulate the continuous variables
test$continuous %>%
    mutate(Metric = label,
           Event  = event_name) %>%
    arrange(Event, primary_treatment) %>%
    dplyr::select(Metric, primary_treatment, n, missing, mean_sd, median_iqr, range, -event_name) %>%
    kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
          caption = "EQ5D Visual Analogue Scale and Score by Time-Point and Primary Treatment Group.")

```

#### EORTC QLQ C30

```{r table_eortc_qlq_c30, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
test <- age_gap %>%
        dplyr::filter(event_name == "Baseline") %>%
        dplyr::filter(!is.na(primary_treatment)) %>%
        ungroup() %>%
        ctru::table_summary(df        = .,
                            lookup    = master$lookups_fields,
                            id        = individual_id,
                            select    = c(## ql_scale, pf_scale, rf_scale,
                                          ## ef_scale, cf_scale, sf_scale,
                                          ## fa_scale, nv_scale, pa_scale,
                                          ## dy_scale, sl_scale, ap_scale,
                                          ## co_scale, di_scale, fi_scale,
                                          c30_q1, c30_q2, c30_q3, c30_q4, c30_q5,
                                          c30_q6, c30_q7, c30_q8, c30_q9, c30_q10,
                                          c30_q11, c30_q12, c30_q13, c30_q14, c30_q15,
                                          c30_q16, c30_q17, c30_q18, c30_q19, c30_q20,
                                          c30_q21, c30_q22, c30_q23, c30_q24, c30_q25,
                                          c30_q26, c30_q27, c30_q28),
                            time      = event_name,
                            group     = primary_treatment,
                            nomissing = FALSE,
                            digits    = 2,
                            reshape   = NULL)
## Reshape the factor table and print
spread(test$factor,
       value,
       n_prop,
       fill = "0 (0.00)") %>%
    mutate(Dimension = label,
           Event     = event_name) %>%
    ## You can reorder this table by choosing which of the two lines below you wish to order by
    arrange(Dimension, primary_treatment, event_name) %>%
    ## arrange(Dimension, event_name, primary_treatment) %>%
    dplyr::select(Dimension, primary_treatment, Event,
                  `Not at All`, `A Little`, `Quite a Bit`, `Very Much`, `<NA>`, -event_name, -label) %>%
    kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
          caption = "EORTC QLQ C30 Domains at Baseline by Primary Treatment Group.")
## Tabulate the continuous variables
## test$continuous %>%
##     mutate(Metric = label) %>%
##     dplyr::select(Metric, primary_treatment, n, missing, mean_sd, median_iqr, range, -event_name) %>%
##     kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
##           caption = "EORTC QLQ C30 Scaled Scores by Time-Point and Primary Treatment Group.")

```


#### EORTC QLQ BR23

```{r table_eortc_qlq_br23, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
test <- age_gap %>%
        dplyr::filter(!is.na(primary_treatment)) %>%
        ungroup() %>%
        ctru::table_summary(df        = .,
                            lookup    = master$lookups_fields,
                            id        = individual_id,
                            select    = c(## brbi_scale, brsee_scale, brfu_scale,
                                          ## brst_scale, brbs_scale, bras_scale,
                                          ## brhl_scale,
                                          br23_q31, br23_q32, br23_q33, br23_q34, br23_q35,
                                          br23_q36, br23_q37, br23_q38, br23_q39, br23_q40,
                                          br23_q41, br23_q42, br23_q43, br23_q44, br23_q45,
                                          br23_q46, br23_q47, br23_q48, br23_q49, br23_q50,
                                          br23_q51, br23_q52, br23_q53),
                            time      = event_name,
                            group     = primary_treatment,
                            nomissing = FALSE,
                            digits    = 2,
                            reshape   = NULL)
## Reshape the factor table and print
spread(test$factor,
       value,
       n_prop,
       fill = "0 (0.00)") %>%
    mutate(Dimension = label,
           Event     = event_name) %>%
    ## You can reorder this table by choosing which of the two lines below you wish to order by
    arrange(Dimension, primary_treatment, event_name) %>%
    ## arrange(Dimension, event_name, primary_treatment) %>%
    dplyr::select(Dimension, primary_treatment, Event,
                  `Not at All`, `A Little`, `Quite a Bit`, `Very Much`, `<NA>`, -event_name, -label) %>%
    kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
          caption = "EORTC QLQ BR23 Domains by Time-Point and Primary Treatment Group.")
## Tabulate the continuous variables
## test$continuous %>%
##     mutate(Metric = label) %>%
##     dplyr::select(Metric, primary_treatment, n, missing, mean_sd, median_iqr, range, -event_name) %>%
##     kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
##           caption = "EORTC QLQ BR23 scaled scores by Time-Point and Primary Treatment Group.")

```


#### EORTC QLQ ELD15

```{r table_eortc_qlq_eld15, echo = FALSE, cache = FALSE, fig.width = 8, fig.height = 8,eval = TRUE}
## Table
test <- age_gap %>%
        dplyr::filter(!is.na(primary_treatment)) %>%
        ungroup() %>%
        ctru::table_summary(df        = .,
                            lookup    = master$lookups_fields,
                            id        = individual_id,
                            select    = c(## mo_scale, wao_scale, wo_scale,
                                          ## mp_scale, boi_scale, fs_scale,
                                          ## js_scale,
                                          eld15_q54, eld15_q55, eld15_q56, eld15_q57, eld15_q58,
                                          eld15_q59, eld15_q60, eld15_q61, eld15_q62, eld15_q63,
                                          eld15_q64, eld15_q65, eld15_q66, eld15_q67, eld15_q68),
                            time      = event_name,
                            group     = primary_treatment,
                            nomissing = FALSE,
                            digits    = 2,
                            reshape   = NULL)
## Reshape the factor table and print
spread(test$factor,
       value,
       n_prop,
       fill = "0 (0.00)") %>%
    mutate(Dimension = label,
           Event     = event_name) %>%
    ## You can reorder this table by choosing which of the two lines below you wish to order by
    arrange(Dimension, primary_treatment, event_name) %>%
    ## arrange(Dimension, event_name, primary_treatment) %>%
    dplyr::select(Dimension, primary_treatment, Event
                  `Not at All`, `A Little`, `Quite a Bit`, `Very Much`, `<NA>`, -event_name, -label) %>%
    kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
          caption = "EORTC QLQ BR23 Domains by Time-Point and  Primary Treatment Group.")
## Tabulate the continuous variables
## test$continuous %>%
##     mutate(Metric = label) %>%
##     dplyr::select(Metric, primary_treatment, n, missing, mean_sd, median_iqr, range, -event_name) %>%
##     kable(col.names = gsub("primary_treatment", "Primary Treatment", names(.)),
##           caption = "EORTC QLQ BR23 scaled scores by Time-Point and  Primary Treatment Group.")

```
